TRITON: Globally Consistent Sim-to-Real Transfer ``I can't believe it's not real!"

### 2022-06-08 CORL/example.tex
I can't believe it's not real!
Added Ryoo's advice

\title{TRITON: Globally Consistent Sim-to-Real Transfer}

@@

@@

\section{Data}
\label{sec:data}

>>>>

\title{TRITON: Globally Consistent Sim-to-Real Transfer

``I can't believe it's not real!" %Definitely gonna delete this lol
 %via Neural Textures
 }

@@

TODO: Note that the simple input of UVL, or an RGB neural texture, means any simulator should be plug-and-play with this algorithm.

@@

\section{Formulation}
\label{sec:data}

TODO: Describe what UVL is ; 
Formulate the setting: What our inputs are and the targets are and what we learn (a neural texture function) and how we can take advantage of it for robotic learning.
Don't go into details; just say 'its a black box function'

TODO: Create subfigures with subcaptions. 
2a: Nothing but UVL=UV+L
2b. 3d uvl axis to texture pack (drew on whiteboard)
2c. Skip over the translation network and show a pretty robot arm picture

This is the formulatoin section; not data section. Dont talk about how many photos we use etc.

JUST IN CASE THINGS ARE ERASED:
We learn neural texture corresponding to each object, where each texture is represented as a function mapping... 
The idea is to learn object textures as a set of continuous functions from a set of (unlabeled) real images, and use them to generate realistic images.
Given a 3D structure of the scene represented with a UVL image, the learned neural textures will translate them into a realistic image.
When used for the robot learning, this enables learnable, realistic sim2real of robot training images.

IN THE INTRODUCTION: How we're using a neural neural network network texture. Also in related works.

TODO: Replace neural texture in figure 3 with axis, and treat it as a function that takes UV in with an arrow pointing to it.

BREAK IT DOWN APPROACH:
Don't have any pictures. Have breakdown where we add new things in multiple figures.
First figure: Just image translation. 
Seconf:
Third:
Etc...

\begin{equation}
	\label{eq:somename}
	Do stuff like this

\end{equation}
